\documentclass[10pt]{article}

\usepackage{calc}
\usepackage{comment}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em} %1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
%        {\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{enumerate}\vspace{-.6\baselineskip}}
%        {\end{list}\vspace{-.6\baselineskip}}
\makeatother
\reversemarginpar

\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[1]{\pagebreak[3]%
    \hyphenpenalty=10000%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}}

\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}\vspace{-.6\baselineskip}}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

\providecommand*\url[1]{\href{#1}{#1}}
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}
\providecommand*\email[1]{\href{mailto:#1}{#1}}

\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    \TeX}}
\providecommand\Matlab{\textsc{Matlab}}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\makeheading{Nakul Garg}

\section{Contact Information}

\newlength{\rcollength}\setlength{\rcollength}{1.4in}%


A-36, Ashoka Encalve  \hfill {Contact : +91 8800 565859} \newline
Peeragarhi \hfill {e-mail id : \email{nakulgarg.2208@gmail.com}} \newline
New Delhi, 110087\hfill  \href{https://github.com/Nakul22}{git : https://github.com/Nakul22} \newline
INDIA \hfill \href{https://goo.gl/bs3Snq}{website : https://sites.google.com/view/nakulgarg/}

\section{Education}
\textbf{I.P.U.},
New Delhi, India \hfill{Aug. 2014--May 2018}\\
B.Tech. in ECE, 70\%, Converted GPA 4.0\\
\textbf{S.M.S.},
New Delhi, India \\
12\textsuperscript{th} C.B.S.E, 90\%\hfill{Jul. 2014}\\
10\textsuperscript{th} C.B.S.E, 82\%\hfill{Jul. 2012}

\section{Selected Publications}
\textbf{N. Garg}, A. Anand, B. Chagglani, A. Ashok, ``Visible Light Communication in Drones," (in submission), 2019.\\
\textbf{N. Garg}, I. Janveja, D. Malhotra, C. Chawla, P. Gupta, H. Bansal, A. Chowdhery, P. Mukherjee, and Brejesh Lall, ``DRIZY- An IOT based Driver Assistance System," (in submission), 2018.\\
I. Janveja, \textbf{N. Garg}, C. Chawla, J.Parikh. ``Aquacomm: Underwater Visible Light Communication," IndiaCom, India, 2018.\\
\textbf{N. Garg}, I. Janveja, D. Malhotra, C. Chawla, P. Gupta, H. Bansal, A. Chowdhery, P. Mukherjee, and Brejesh Lall. ``DRIZY---Collaborative Driver Assistance Over Wireless Networks," \textbf{ACM MobiCom} Poster, Utah, USA, 2017.\\
\textbf{N. Garg}, J.Parikh. ``Wireless transceiver design for visible light communication," ICICI, India, 2017.

\section{Filed Patents}
\textbf{N. Garg} ``Advanced IoT based Home Automation System without Rewiring", 2016. Intellectual Property India Serial No. 201711020040

\section{Experience}
\textbf{Research Fellow} \hfill {Sept. 2018---Present}\\
CSE Department, IIT Delhi\\
\emph{Advised by :}, \href{http://www.cse.iitd.ernet.in/~rijurekha/index.html}{Dr. Rijurekha Sen} (IIT Delhi) and \href{http://isn.ucsd.edu/~siddharth/}{Dr. Siddharth Joshi} (Notre Dame)\\
\textbf{Technical Advisor} \hfill {May. 2018---Sept. 2018}\\
Celestini Project India, Marconi Society, Google, IIT Delhi\\
\emph{Led by :}, \href{http://www.achowdhery.com/}{Dr. Aakanksha Chowdhery} (Google AI) and \href{http://ee.iitd.ernet.in/people/brijeshlall.html}{Dr. Brejesh Lall} (IIT Delhi)\\
\textbf{Project Intern} \hfill {Jun. 2017---Sept. 2017}\\
Celestini Project India, Marconi Society, Google, IIT Delhi\\
\emph{Led by :}, \href{http://www.achowdhery.com/}{Dr. Aakanksha Chowdhery} (Google AI) and \href{http://ee.iitd.ernet.in/people/brijeshlall.html}{Dr. Brejesh Lall} (IIT Delhi)\\
\textbf{Technical Executive} \hfill {Aug. 2016---Jul. 2017}\\
Robotime Robotics Lab (STEM in schools)\\
\textbf{Trainee} \hfill {Sept. 2015---May 2016}\\
Embedded Systems, IQB Solutions, Delhi

\section{Positions of Responsibility}
\textbf{Chairperson} BVP IEEE Student Branch \hfill {2017 - 18}
\begin{innerlist}
\item Led a team of 200 students to organize one of the biggest technical hackathon in Delhi, India.
\end{innerlist}
\textbf{Vice--Chair} of Robotics Society, BVCOE \hfill {2016 - 17}
\begin{innerlist}
\item Conducted workshops across India to teach programming concepts on Arduino/Raspberry, Image Processing and Project Management to 200+ students.
\end{innerlist}
\textbf{Head Event--Manager}, Fervour - Technical Fest of college. \hfill {2017}
\begin{innerlist}
\item Organized 17 technical events in campus with an outreach of 1000+ students in India.
\end{innerlist}

\section{Awards and Scholarships}
\begin{innerlist}
\item Outstanding Student Volunteer Award by IEEE Delhi Section. \hfill 2018
\item First position at \textbf{EV Hackathon}, India - Australia joint initiative. \hfill 2018
\item Winner of World Food India Hackathon. Awarded by \textbf{President of India}. \hfill 2017
\item  Winner of Celstini Project India 2017,IIT Delhi & Marconi Society. Sponsored by Google.(URL: \href{http://www.celestiniprojectindia.com}{www.celestiniprojectindia.com}) \hfill 2017
\item Travel grants: NSF for Mobicom 2017, \textbf{ACM SIGMOBILE}\hfill 2017
\item 1\textsuperscript{st} in \textbf{eYantra - National Robotics Competition}, \textbf{IIT Bombay}\hfill 2017
\item 2\textsuperscript{nd} in \textbf{eYantra - National Robotics Competition}, \textbf{IIT Bombay}\hfill 2016
\item Ranked 44 in \textbf{IEEE XTreme Hackathon}\hfill  2015
\item 1\textsuperscript{st} in Robotron TechMarathon, DDUC, Delhi University\hfill 2014
\item Among top 6 in \textbf{National CBSE Science Exhibition}\hfill  2013
\item 4\textsuperscript{th} in \textbf{International Quanta}, CMS School, Lucknow\hfill 2013
\item 1\textsuperscript{st} in \textbf{Regional level CBSE Science Exhibition}\hfill  2012
\item 1\textsuperscript{st} in Annual School Science Exhibition\hfill 2011
\item 1\textsuperscript{st} in Annual School Science Exhibition\hfill  2010
\item 2\textsuperscript{nd} in Annual School Science Exhibition\hfill  2009
\end{innerlist}

\section{Technical Projects}
\begin{innerlist}
    \item \textbf{"Near Sensor ML"} Reducing latency by bringing ML at edge. \hfill {2018}
    \item \textbf{"PlugFree"} Autonomous charging of Drones. (Sponsored by GSU, USA) \hfill {2018}
    \item \textbf{"Augur"} Visible Light Communication using Smartphone Camera \hfill {2018}
    \item \textbf{"DRIZY"} Collaborative Driver Assistance Over Wireless Networks \hfill {2017}
    \item \textbf{Li-Fi} (Data transfer through light) Demonstration \hfill {2017}
    \item \textbf{"PUSHPAK"} Aerial Surveillance Quadcopter with Rover\hfill {2016}
    \item \textbf{Touch--Screen} Based Home Automation \hfill {2016}
    \item \textbf{IOT} based Temperature Logger with Remote Access\hfill {2016}
    \item \textbf{FireBird V Robot} -- Mars Rover Navigation and 3D Modelling\hfill {2016}
    \item Raspberry pi-3 based Personal \textbf{Cloud Storage} \hfill {2015}
    \item Anti Car Theft System with SMS alert application\hfill {2014}
    \item \textbf{Zig--Bee} based Swarm Robotics\hfill {2014}
    \item Automatic Rubik’s Cube Solver\hfill {2014}
    \item \textbf{Wireless Odometer}\hfill {2012}
\end{innerlist}

\section{Research Interests}
Visible Light Communication, Mobile Computing, Robotics, Sensing, HCI

\section{Skills and \\Tools}
Languages : C/C++, Python, MATLAB, OpenCV, \LaTeX, Verilog\\
Technologies : Arduino, Raspberry Pi, Deep Learning, Computer Vision

\section{Society Memberships}
Institute of Electrical and Electronics Engineers (IEEE)\\
Association for Computing Machinery (ACM)

\end{document}