\documentclass[10pt]{article}
\usepackage{calc}
\usepackage{comment}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em} %1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
%        {\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{enumerate}\vspace{-.6\baselineskip}}
%        {\end{list}\vspace{-.6\baselineskip}}
\makeatother
\reversemarginpar

\usepackage{textcomp}

\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage[shortlabels]{enumitem}

\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
%\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

%%%%%%%%%%%%%%%%%%%%%%%% End Document Setup %%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%% Helper Commands %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\makeheading}[2][]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries #2 \hfill #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[1]{\pagebreak[3]%
    \hyphenpenalty=10000%
    \vspace{1.3\baselineskip}%
    \phantomsection\addcontentsline{toc}{section}{#1}%
    \noindent\llap{\scshape\smash{\parbox[t]{\marginparwidth}{\raggedright #1}}}%
    \vspace{-\baselineskip}\par}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}}

\newenvironment{loneinnerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt]}
        {\end{itemize}\vspace{-.6\baselineskip}}

\newcommand{\blankline}{\quad\pagebreak[3]}
\newcommand{\halfblankline}{\quad\vspace{-0.5\baselineskip}\pagebreak[3]}

\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}

\providecommand*\url[1]{\href{#1}{#1}}
\renewcommand*\url[1]{\href{#1}{\texttt{#1}}}
\providecommand*\email[1]{\href{mailto:#1}{#1}}

\providecommand\BibTeX{{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    \TeX}}
\providecommand\Matlab{\textsc{Matlab}}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
% {
% \centering
% \makeheading{Nakul Garg}
% }
%\begin{center}
{\LARGE {\bf \hspace{1.5in}Nakul Garg\vspace{0.2in}}}
%\end{center}

\section{\textbf{Contact Information}}

\newlength{\rcollength}\setlength{\rcollength}{1.4in}%


3245 Brendan Iribe Center \hfill {+1 202-725-1919} \newline
8125 Campus Drive \hfill {\email{nakul22@umd.edu}} \newline
College Park, MD 20742 \hfill \href{https://www.cs.umd.edu/~nakul}{https://www.cs.umd.edu/\~{}nakul/} 
% \newline

\vspace{0.1in}
\section{\textbf{Research Interests}}
%Mobile Computing, Wireless Networking, Low-power sensing, Underwater IoT\\
Ultra-low-power Sensing, Ambient Sensing, Embedded AI, Ubiquitous Perception\\

\section{\textbf{Education}}
\textbf{Ph.D.}, Computer Science \hfill{2019--present}\\
University of Maryland, College Park\\

\textbf{Bachelor of Technology}, ECE \hfill{2014--2018}\\
Guru Gobind Singh Indraprastha University

%\textbf{St. Marks School},
%New Delhi, India \\
%12\textsuperscript{th} C.B.S.E, 90\%\hfill{Jul. 2014}\\
%10\textsuperscript{th} C.B.S.E, 82\%\hfill{Jul. 2012}


\section{\textbf{Awards \& Honors}}
\begin{innerlist}
\item SPiDR is the SIGMOBILE research highlight \hfill 2023
\item Ann G. Wylie Dissertation Fellowship \hfill 2023
\item Future Faculty Fellowship \hfill 2023
\item Outstanding Graduate Assistant Award \hfill 2023
\item Best paper award MobiSys \hfill 2022
\item Three minute Thesis (3MT) Award \hfill 2022
\item Owlet featured on cover of ACM GetMobile, June'21 \hfill 2021
\item Best demo award MobiSys \hfill 2021
\item University of Maryland CS Summer Research Fellowship \hfill 2021
\item Travel grant HotMobile, ACM SIGMOBILE\hfill 2020
\item University of Maryland Graduate School Dean's Fellowship \hfill 2019
\item Outstanding Student Volunteer Award by IEEE Delhi Section. \hfill 2018
% \item First position at EV Hackathon, India - Australia joint initiative. \hfill 2018
\item Winner of World Food India Hackathon. Awarded by President of India. \hfill 2017
\item  Winner of Celestini Project India 2017, IIT Delhi \& Marconi Society. \hfill 2017
\item Travel grant Mobicom'17, NSF, ACM SIGMOBILE\hfill 2017
\item Winner of eYantra - National Robotics Competition, IIT Bombay\hfill 2017
% \item 2\textsuperscript{nd} in eYantra - National Robotics Competition, IIT Bombay\hfill 2016
% \item Ranked 44 in \textbf{IEEE XTreme Hackathon}\hfill  2015
% \item 1\textsuperscript{st} in Robotron TechMarathon, DDUC, Delhi University\hfill 2014
\end{innerlist}


\section{\textbf{Publications}}

% [Under submission] A work on ultra-low-power self-localization using a single receiver antenna\\
% \textbf{Nakul Garg}, Aritrik Ghosh, Nirupam Roy\\
% NSDI 2023\\

Structure Assisted Spectrum Sensing for Low-power Acoustic Event Detection\\
\textbf{Nakul Garg}, Harshvardhan Takawale, Yang Bai, Irtaza Shahid, Nirupam Roy\\
IASA CPS IoT Week 2023\\

ThermWare: Towards Side-channel Defense for Tiny IoT Devices\\
\textbf{Nakul Garg}, Irtaza Shahid, Erin Avllazagaj, Jennie Hill, Jun Han, Nirupam Roy\\
HotMobile 2023\\

Poster: Bringing AR/VR to Everyday Life- A Wireless Localization perspective\\
\textbf{Nakul Garg}, Irtaza Shahid, Karthik Sankar, Mallesham Dasari, Ram Sheshadri, Karthikeyan Sundaresan, Nirupam Roy\\
HotMobile 2023\\

Poster: Natural Voice Interface for the Next Generation of Smart Spaces\\
Yang Bai, \textbf{Nakul Garg}, Harshvardhan Takawale, Anupam das, Nirupam Roy\\
HotMobile 2023\\
\\

SPiDR: Ultra-low-power Acoustic Spatial Sensing for Micro-robot Navigation\\
Yang Bai, \textbf{Nakul Garg (co-primary)}, Nirupam Roy\\
Mobisys 2022\\

Poster: Ultra-low-power Acoustic Imaging\\
Yang Bai, \textbf{Nakul Garg (co-primary)}, Nirupam Roy\\
Mobisys 2022\\

VoiceFind: Noise-Resilient Speech Recovery in Commodity Headphones\\
Irtaza Shahid, Yang Bai, \textbf{Nakul Garg}, Nirupam Roy\\
IASA Workshop Mobisys 2022\\

Owlet: Enabling Spatial Information in Ubiquitous Acoustic devices\\
\textbf{Nakul Garg}, Yang Bai (co-primary), Nirupam Roy\\
Mobisys 2021\\

Demo: Microstructure-guided Spatial Sensing for Low-power IoT\\
\textbf{Nakul Garg}, Yang Bai (co-primary), Nirupam Roy\\
Mobisys 2021\\

Enabling Self-defense in Small Drones\\
\textbf{Nakul Garg}, Nirupam Roy\\
HotMobile 2020\\

Poster: Acoustic Sensing for Detecting Projectile Attacks on Small Drones\\
\textbf{Nakul Garg}, Nirupam Roy\\
HotMobile 2020\\

Evaluating LED-Camera Communication for Drones\\
Bhawana Chhaglani, Abhay Sheel Anand, \textbf{Nakul Garg}, Ashwin Ashok\\
LioT Workshop Mobicom 2020\\

Poster: DRIZY- Collaborative Driver Assistance Over Wireless Networks\\
\textbf{Nakul Garg}, Ishani Janveja, Divyansh Malhotra, Chetan Chawla, Pulkit Gupta, Harshil Bansal, Aakanksha Chowdhery, Prerana Mukherjee, Brejesh Lall\\
MobiCom 2017
%\textbf{N. Garg}, I. Janveja, D. Malhotra, C. Chawla, P. Gupta, H. Bansal, A. Chowdhery, P. Mukherjee, and Brejesh Lall. ``DRIZY---Collaborative Driver Assistance Over Wireless Networks," \textbf{ACM MobiCom} Poster, Utah, USA, 2017.


\section{\textbf{Experience}}
\textbf{Research Intern} \hfill {May. 2022---Aug. 2022}\\
NEC Laboratories\\
\emph{Advised by :} \href{https://sites.google.com/view/karthik-s}{Prof. Karthik Sundaresan}, \href{https://sites.google.com/view/ram-sheshadri/home}{Dr. Ramanujan K Sheshadri}\\

\textbf{Research Intern} \hfill {Sept. 2018---July 2019}\\
Computer Science Department, IIT Delhi\\
\emph{Advised by :} \href{http://www.cse.iitd.ernet.in/~rijurekha/index.html}{Dr. Rijurekha Sen}\\

\textbf{Technical Advisor} \hfill {May 2018---Sept. 2018}\\
Celestini Project India, Marconi Society, Google, IIT Delhi\\
\emph{Led by :} \href{http://www.achowdhery.com/}{Dr. Aakanksha Chowdhery} (Google AI) and \href{http://ee.iitd.ernet.in/people/brijeshlall.html}{Dr. Brejesh Lall} (IIT Delhi)\\

\textbf{Research Intern} \hfill {Jun. 2017---Sept. 2017}\\
Celestini Project India, Marconi Society, Google, IIT Delhi\\
\emph{Advised by :} \href{http://www.achowdhery.com/}{Dr. Aakanksha Chowdhery} (Google AI) and \href{http://ee.iitd.ernet.in/people/brijeshlall.html}{Dr. Brejesh Lall} (IIT Delhi)\\

\section{\textbf{Selected Talks}}
\textbf{Talk:} Ultra-low-power Perception for Micro-robots\\
Sept 9, 2022\\
Maryland Robotics Center\\

\textbf{Invited Talk:} Toward Battery-free robots\\
April 26, 2022\\
First-Year Innovation \& Research Experience, UMD\\

\textbf{3MT:} Inventing Battery-free Devices for a Sustainable Present\\
April 6, 2022\\
University of Maryland College Park, USA\\

\textbf{Invited Talk:} Powering up the Next Generation of Robots\\
Nov 16, 2021\\
First-Year Innovation \& Research Experience, UMD\\

\textbf{Invited Talk:} Owlet: Enabling Spatial Information in Ubiquitous Acoustic devices\\
July 19, 2021\\
Stony Brook University (Online)\\

\textbf{Invited Talk:} Owlet: Enabling Spatial Information in Ubiquitous Acoustic devices\\
July 15, 2021\\
University of Illinois Urbana-Champaign (Online)\\

\textbf{Talk:} Owlet: Enabling Spatial Information in Ubiquitous Acoustic devices\\
July 2, 2021\\
Mars, Solar System, Milky way (Online)\\

\section{\textbf{Teaching}}
Workshop: TinyML and TensorFlow Lite, 2022\\

CMSC715 Wireless and Mobile Systems for the IoT, Fall'21, Fall'22\\
Instructor: Prof. Nirupam Roy\\

Workshop: Introduction to Matlab, 2021\\

CMSC420 Advanced Data Structures, Fall'19, Spring'21\\
Instructor: Prof. David Mount\\

CMSC818W Wireless and Mobile Systems for the IoT, Fall'20\\
Instructor: Prof. Nirupam Roy\\

CMSC417 Computer Networks, Spring'20\\
Instructor: Prof. Nirupam Roy\\

Workshop Series: Embedded AI and Robotics, 2016-18\\

% CMSC420 Advanced Data Structures, Fall'19\\
% Instructor: Prof. Jason Filippou\\

%\section{Positions of Responsibility}
%\textbf{Chairperson} BVP IEEE Student Branch \hfill {2017 - 18}
%\begin{innerlist}
%\item Led a team of 200 students to organize one of the biggest technical hackathon in Delhi, India.
%\end{innerlist}
%\textbf{Vice--Chair} of Robotics Society, BVCOE \hfill {2016 - 17}
%\begin{innerlist}
%\item Conducted workshops across India to teach programming concepts on Arduino/Raspberry, Image Processing and Project Management to 200+ students.
%\end{innerlist}
%\textbf{Head Event--Manager}, Fervour - Technical Fest of college. \hfill {2017}
%\begin{innerlist}
%\item Organized 17 technical events in campus with an outreach of 1000+ students in India.
%\end{innerlist}


\section{\textbf{Media Coverage}}
\begin{innerlist}
\item Owlet: ACM GetMobile
\item DopplerDodge: The Economist, Robotics Industry News, ...
\item Aerogram: Times of India, Hindustan Times, ...
\end{innerlist}

\section{\textbf{Activities \& Services}}
\begin{innerlist}
\item Shadow TPC Sensys'22
\item Reviewer IEEE Transactions on Mobile Computing
\item Mentor at Bitcamp Research Trail 2021. An initiative to engage BIPOC students in research.
\item President of the IEEE student chapter at BVP in the academic year 2017-18.
\item Chairperson of the Robotics and Automation Society. Conducted 20 workshops in the academic year 2016-17.
\end{innerlist}


%\section{Technical Projects}
%\begin{innerlist}
%    \item \textbf{"Aerogram"} Particualte Matter Sensor Network in 200 Buses across Delhi. \hfill {2019}
%    \item \textbf{"Near Sensor ML"} Reducing latency by bringing ML at edge. \hfill {2018}
%    \item \textbf{"PlugFree"} Autonomous charging of Drones. (Sponsored by GSU, USA) \hfill {2018}
%    \item \textbf{"Augur"} Visible Light Communication using Smartphone Camera \hfill {2018}
%    \item \textbf{"DRIZY"} Collaborative Driver Assistance Over Wireless Networks \hfill {2017}
%    \item \textbf{Li-Fi} (Data transfer through light) Demonstration \hfill {2017}
%    \item \textbf{"PUSHPAK"} Aerial Surveillance Quadcopter with Rover\hfill {2016}
%    \item \textbf{Touch--Screen} Based Home Automation \hfill {2016}
%    \item \textbf{IOT} based Temperature Logger with Remote Access\hfill {2016}
%    \item \textbf{FireBird V Robot} -- Mars Rover Navigation and 3D Modelling\hfill {2016}
%    \item Raspberry pi-3 based Personal \textbf{Cloud Storage} \hfill {2015}
%    \item Anti Car Theft System with SMS alert application\hfill {2014}
%    \item \textbf{Zig--Bee} based Swarm Robotics\hfill {2014}
%    \item Automatic Rubik’s Cube Solver\hfill {2014}
%    \item \textbf{Wireless Odometer}\hfill {2012}
%\end{innerlist}

%\section{Skills and \\Tools}
%Languages : C/C++, Python, MATLAB, OpenCV, \LaTeX, Verilog\\
%Technologies : Arduino, Raspberry Pi, Deep Learning, Computer Vision
%
%\section{Society Memberships}
%Institute of Electrical and Electronics Engineers (IEEE)\\
%Association for Computing Machinery (ACM)

\end{document}